### 2015-11-20 section/5_exper.tex
check in proofread results

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcc}
    \toprule
                            	&  {\bf Reported}             &{\bf Fix }                     \\
   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
   \midrule
   Mozilla347306                & \Yes                        & \Yes                                          \\
   Mozilla416628                & \Yes                        & \Yes                                         \\
   Mozilla490742$_a$            & \Yes                        & \Yes                                             \\
   Mozilla35294$_a$             & \Yes                          & \Yes                                              \\ 
   Mozilla477564$_a$            & \Yes                          & \Yes                                            \\
   \midrule 
   MySQL27287                   & \Yes                          & \ding{55}                                         \\
   MySQL15811                   & \Yes                          & \Yes                                      \\ 
   \midrule    
   Apache32546                  & \Yes                          & \Yes                                      \\
   Apache37184$_a$              & \Yes                          & \Yes                                        \\
   Apache29742$_a$              & \Yes                          & \Yes                                       \\ 
   Apache34464                  & \Yes                          & \Yes                                        \\
   Apache47223                  & \Yes                          & \Yes                                       \\
   \midrule
   GCC46401                     & \Yes                     & \Yes                                      \\
   GCC1687                      & \Yes                          & \Yes                                     \\
   GCC27733$_a$                 & \Yes                          & \Yes                                     \\
   GCC8805                      & \Yes                          & \Yes                                  \\
   GCC21430                     & \Yes                          & \Yes                                     \\
   GCC12322                     & \Yes                         & \ding{55}                                   \\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Coverage Results.}
  \label{tab:cover}
\end{table}

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
the fix strategy that developers used. For MySQL27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
find a new data structure that can eliminate both root causes.
For GCC12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the slow-down caused by the original loop.

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294$_a$      &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564$_a$     &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742$_a$       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733$_a$          &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

\Tool can also help improve the accuracy of statistical debugging in
identifying which loop is the root cause loop.
For example, the real root-cause loop of Apache34464 and GCC 46401 both
rank number two by the statistical performance diagnosis tool.
Fortunately,
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy.

@@

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733$_a$    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla347306. We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
As we will discuss later, 
the current diagnosis results are obtained by running the
program only \textbf{once} under the problem-triggering workload.
If we use sparser sampling, more failure runs will be needed to obtain good
diagnosis results.

@@

The benefit of static optimization is also non-trivial. 
For example, for MySQL15811 and MySQL27287, static analysis alone can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are natually different
in different iterations. Consequently, run-time overhead is completely
eliminated for these two benchmarks.
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
Mozilla347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC8805 and GCC12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
Mozilla347306 has the largest overhead (4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

>>>>

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcc}
    \toprule
                            	&  {\bf Reported}             &{\bf Fix }                     \\
   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
   \midrule
   Mozilla347306                & \Yes                        & \Yes                                          \\
   Mozilla416628                & \Yes                        & \Yes                                         \\
   Mozilla490742                & \Yes                        & \Yes                                             \\
   Mozilla35294                 & \Yes                          & \Yes                                              \\ 
   Mozilla477564                & \Yes                          & \Yes                                            \\
   \midrule 
   MySQL27287                   & \Yes                          & \ding{55}                                         \\
   MySQL15811                   & \Yes                          & \Yes                                      \\ 
   \midrule    
   Apache32546                  & \Yes                          & \Yes                                      \\
   Apache37184                  & \Yes                          & \Yes                                        \\
   Apache29742                  & \Yes                          & \Yes                                       \\ 
   Apache34464                  & \Yes                          & \Yes                                        \\
   Apache47223                  & \Yes                          & \Yes                                       \\
   \midrule
   GCC46401                     & \Yes                     & \Yes                                      \\
   GCC1687                      & \Yes                          & \Yes                                     \\
   GCC27733                     & \Yes                          & \Yes                                     \\
   GCC8805                      & \Yes                          & \Yes                                  \\
   GCC21430                     & \Yes                          & \Yes                                     \\
   GCC12322                     & \Yes                         & \ding{55}                                   \\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Coverage Results.}
  \label{tab:cover}
\end{table}

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
the fix strategy that developers used. For MySQL\#27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
find a new data structure that can eliminate both root causes.
For GCC\#12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the slow-down caused by the original loop.

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

\Tool can also help improve the accuracy of statistical debugging in
identifying which loop is the root cause loop.
For example, the real root-cause loop of Apache\#34464 and GCC\#46401 both
rank number two by the statistical performance diagnosis tool.
Fortunately,
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy.

@@

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

@@

As shown in Table \ref{tab:performance}, 
the performance of \Tool is good. The overhead is consistently under or around 5\% 
except for one benchmark, Mozilla\#347306. We believe \Tool is promising for potential production
run usage.
We can easily further lower the overhead through sparser sampling.
As we will discuss later, 
the current diagnosis results are obtained by running the
program only \textbf{once} under the problem-triggering workload.
If we use sparser sampling, more failure runs will be needed to obtain good
diagnosis results.

@@

The benefit of static optimization is also non-trivial. 
For example, for MySQL\#15811 and MySQL\#27287, static analysis alone can
judge that they do not contain cross-iteration redundancy: the computation of 
each iteration depends on loop induction variables, which are natually different
in different iterations. Consequently, run-time overhead is completely
eliminated for these two benchmarks.
As another example, the buggy loops of MySQL\#27287 and MySQL\#15811 access 
arrays. 
After changing to tracking the initial and ending memory-access addresses
of the array, instead of the content of the whole array accesses,
the overhead is reduced from 11.77\% to 1.66\% for MySQL\#27287, 
and from 20.46\% to 0.03\% for MySQL\#15811 respectively 
(sampling is conducted consistently here).

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
Mozilla\#347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC\#8805 and GCC\#12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
Mozilla\#347306 has the largest overhead (4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC\#12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.
